---
title: "Homework1"
author: "Avery Wang"
date: 2024-09-19
output: github_document
---

## Problem 1

The first step is to import the necessary packages and dataset. The tidyverse library is used here to call the tibble function.

```{r}
#import tidyverse library 
library(tidyverse)
# import the dataset

data("penguins", package = "palmerpenguins")
```

The description of the penguins dataset: 

* Key variables in the dataset: `r names(penguins)`

  * The penguins dataset include `r length(levels(penguins$species))` different             kinds of species: `r levels(penguins$species)`.
  * The penguins dataset include `r length(levels(penguins$island))` different               kinds of islands: `r levels(penguins$island)`.
  * The dataset include `r length(levels(penguins$sex))` sex types: 
      `r levels(penguins$sex)`. 
  * The dataset include `r length(unique(penguins$year))` different years :
    `r unique(penguins$year)`. 

* The row number of the dataset is `r nrow(penguins)`.

* The number of column is `r ncol(penguins)`.

* The mean of the flipper length is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE),2)` mm.

Then make the scatterplot flipper_length_mm (y) vs bill_length_mm (x) using ggplot

```{r warning=F}
#use ggplot setting flipper_length_mm as y and bill_length_mm as x with geom_point() to make scatterplot
ggplot(penguins, aes(x = bill_length_mm, 
                     y = flipper_length_mm,
                     color = species)) + geom_point()
#save the scatter plot with the name scatter_plot.pdf and specify the height and width 
ggsave("scatter_plot.pdf", height = 6, width = 8)
```


## Problem 2

```{r}
#set the seed to make sure numbers can be reproduced
set.seed(123)
#use tibble function and create the dataframe naming df
df=tibble(
  #set a random sample of size 10 from a standard Normal distribution
  random_sample=rnorm(10),
  #a logical vector indicating whether >0
  logical_vector=rnorm(10)>0,
  #a character vector of length 10
  char_vec=c("Amy", "Tony", "Joy", "John", 
             "Michael", "Emma" ,"Lucy","Elsa",
             "Roy","Eva"),
  #a factor vector of length 10, 3 different levels
  factor_vec=factor(c("fail", "good", "excellent", 
               "good", "fail", "excellent", 
              "excellent","good", "fail", "good"))

)
```


Then take the mean of each variable with mean() and pull():

```{r}
#take the mean of random_sample
mean(pull(df, random_sample))
```

```{r}
#take the mean of the logical_vector
mean(pull(df,logical_vector))
```

```{r}
#take the mean of char_vec
mean(pull(df,char_vec))
```

```{r}
#take the mean of variable factor_vec
mean(pull(df,factor_vec))
```

From the codes above, the variables logical_vector and random_sample work. But char_vec and factor_vec cannot work

```{r, warning=FALSE}
#convert logical to numeric
numeric_logical= as.numeric(df$logical_vector)
#convert character to numeric
numeric_char=as.numeric(df$char_vec)
#convert factor to numeric 
numeric_factor=as.numeric(df$factor_vec)
```


* When converting logical to numeric, it successfully creates a numeric vector because TRUE becomes 1 and FALSE becomes 0.
* When converting character to numeric, it fails and resulting in NA since characters cannot be directly coerced to numbers.
* When converting factor to numeric, it successfully creates a numeric vector because factors are categorical variables with underlying integer.

When calculating means, it explains what happens, because it shows the way of  converting to 1 and 0 when taking the means of logical vectors. And character vector cannot be converted which is the reason that mean cannot be calculated here. And for the factor, even though it now gets a number, the number is still meaningless in the context of categorical data. So it leads to NA when taking the mean of the factor vector. 



