---
title: "Homework1"
author: "Avery Wang"
date: 2024-09-19
output: github_document
---

## Problem 1

The first step is to import the necessary packages and dataset. The tidyverse library is used here to call the tibble function.

```{r}
#import tidyverse library 
library(tidyverse)
# import the dataset

data("penguins", package = "palmerpenguins")
```

The description of the penguins dataset: 

* Key variables in the dataset: `r names(penguins)`

  * The penguins dataset include `r length(levels(penguins$species))` different             kinds of species: `r levels(penguins$species)`.
  * The penguins dataset include `r length(levels(penguins$island))` different               kinds of islands: `r levels(penguins$island)`.
  * The dataset include `r length(levels(penguins$sex))` sex types: 
      `r levels(penguins$sex)`. 
  * The dataset include `r length(unique(penguins$year))` different years :
    `r unique(penguins$year)`. 

* The row number of the dataset is `r nrow(penguins)`.

* The number of column is `r ncol(penguins)`.

* The mean of the flipper length is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE),2)` mm.

Then make the scatterplot flipper_length_mm (y) vs bill_length_mm (x) using ggplot

```{r warning=F}
#use ggplot setting flipper_length_mm as y and bill_length_mm as x with geom_point() to make scatterplot
ggplot(penguins, aes(x = bill_length_mm, 
                     y = flipper_length_mm,
                     color = species)) + geom_point()
#save the scatter plot with the name scatter_plot.pdf and specify the height and width to be demonstrated
ggsave("scatter_plot.pdf", height = 6, width = 8)
```
